Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-05-26 WRITEUP/ms.tex
added LIR to SED section, i.e. RXJ1131 is considered a LIRG when comparing to Combes+13, but ULIRG in other regards

A fit including the MIR 24\,$\micron$ photometry
is likely an upper limit on the \fir luminosity arising from starburst.
% since the fit include contribution from the AGN (through power-law to MIR)
If we instead fit for a model excluding the 24\,$\micron$ constraint,
two major consequences are immediately apparent.
First, the power-law index is poorly-constrained (see \Tab{SED}).
Second, the steep power-law implies a small contribution
from the power-law regime
to the total IR luminosity as compared to the graybody.
Thus, the \fir luminosity in
this model should, in principle, corresponds to a
lower limit on the cold dust emission.
Using the best-fit parameters
for this model, we find a  \LFIR of 4.72\petm{2.54}{2.26}\E{12}\,\Lsun and a $M_{\rm dust}$ of 11\petm{5}{6}\E{8}\,\Msun.
Again, the inferred quantities are uncorrected for lensing.
%The best-fit SEDs are shown in \Fig{SED} and the
% resulting parameters are listed in \Tab{SED}.

@@

\begin{figure*}[!htbp]
\centering
\includegraphics[width=0.8\textwidth]{../Figures/FullSED.eps}
\caption{SED model fits to the dust photometry of RXJ1131.
WISE flux is slightly higher than the IRAC point, probably due to a smaller
aperture used in IRAC extraction, both of which were taken from the archive.
Spitzer IRAC:
Aperture flux in 5\farcs diameter with aperture correction applied.
Spitzer/MIPS: PSF fit flux, as source size <
native PSF FWHM of 6".
Might want to add NVSS constraints.
The data are not corrected for dust extinction.
\label{fig:SED}}
\end{figure*}

We correct for lensing using the median magnification factor $(\mu_{\rm L}\eq5.5)$
from the CO lens models. This yields a \LFIR of $($6.9\pmm3.6$)$\E{11}\,\Lsun.
Assuming a Salpeter initial
mass function \citep{Salpeter55a}, we find a
SFR of (120\pmm63)\,\Msun\,yr\pmOne using the
standard conversion \citep{Kennicutt98a}.
To place RXJ1131 in context of existing studies,
we compare its properties
with those reported by C13, which is the largest sample of
IR-luminous galaxy at similar redshift
(0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements.
Since C13 adopt a different definition of
\LFIR (40$-$500\micron)\footnote{We also note that the
\fir luminosity in C13 is derived
based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes.},
we derive the \fir luminosity following this convention.
This yields \LFIR of $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)$\,\Lsun and
a SFR of $($150\pmm 70$)$\,\sfrU.
This implies RXJ1131 is considered a LIRG in regards to their
sample, and consequently,
the SFR of RXJ1131 is lower than that of the C13 sample
(SFR\,$>$\,200, with an average of 1200).

@@

\subsubsection{Linewidth \& Sizes}
We find that the linewidths for both components (redshifted and blueshifted)
inferred from a double Gaussian fit to the line profile are
consistent with the C13 sample (FWHM of 370\,\kms). Such linewidths are higher
than local ULIRGs (240\,\kms; \citealt[][]{Solomon97a}).
Since C13 do not have resolved observations, we compare the
gas distribution with local ULIRGs. The CO gas in RXJ1131 is
distributed $\sim$6\,kpc in radius across (in
the source plane), which is more extended than the average in the
sample of disk-like ULIRGs studied by \citet{Ueda14a},
who find an average radius of 3.5\,$\pm$\,2.3\,kpc
(with a range from 1.1 kpc to 9.3 kpc).
% This also indicates that the positive correlation
% in the linewidth-size relation
% holds at intermediate redshifts. Yet we cannot quantify this further
% with the data represented in this paper.

>>>>

A fit including the MIR 24\,$\micron$ photometry
is likely an upper limit on the \fir luminosity arising from starburst.
% since the fit include contribution from the AGN (through power-law to MIR)
If we instead fit for a model excluding the 24\,$\micron$ constraint,
two major consequences are immediately apparent.
First, the power-law index is poorly-constrained (see \Tab{SED}).
Second, the steep power-law implies a small contribution
from the power-law regime
to the total IR luminosity as compared to the graybody.
Thus, the \fir luminosity in
this model should, in principle, corresponds to a
lower limit on the cold dust emission.
Using the best-fit parameters
for this model, we find a total IR luminosity
\LIR (rest-frame 1\,$-$\,1000\,\micron) of 10.28\petm{1.89}{1.97}\E{12}\,\Lsun,
\LFIR of 4.72\petm{2.54}{2.26}\E{12}\,\Lsun and a $M_{\rm dust}$ of 11\petm{5}{6}\E{8}\,\Msun.
Again, the inferred quantities are uncorrected for lensing.
%The best-fit SEDs are shown in \Fig{SED} and the
% resulting parameters are listed in \Tab{SED}.

@@

\begin{figure*}[!htbp]
\centering
\includegraphics[width=0.8\textwidth]{../Figures/FullSED.eps}
\caption{SED models of the IR dust emission toward RXJ1131.
The data are not corrected for lensing magnification and dust extinction.
WISE flux is slightly higher than the IRAC point, probably due to a smaller
aperture used in IRAC extraction,
both of which were taken from the archive.
IRAC: Aperture flux in 5\farcs diameter.
MIPS: use PSF fit flux from archive as source size $<$ PSF FWHM of 6$^{\prime\prime}$.
Might want to add NVSS constraints.
\label{fig:SED}}
\end{figure*}

We correct for lensing using the median magnification
factor $(\mu_{\rm L}\eq5.5)$
from the CO lens models. This yields a \LFIR of $($6.9\pmm3.6$)$\E{11}\,\Lsun.
Assuming a Salpeter initial
mass function \citep{Salpeter55a}, we find a
SFR of (120\pmm63)\,\Msun\,yr\pmOne using the
standard conversion \citep{Kennicutt98a}.
To place RXJ1131 in context of existing studies,
we compare its properties
with those reported by C13, which is the largest sample of
IR-luminous galaxy at similar redshift
(0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements.
Since C13 adopt a different definition of
\LFIR (40$-$500\micron)\footnote{We also note that the
\fir luminosity in C13 is derived
based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes.},
we derive the \fir luminosity following this convention.
This yields \LFIR of $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)$\,\Lsun and
a SFR of $($150\pmm 70$)$\,\sfrU.
This implies that RXJ1131 is considered a LIRG in regard to their
sample, and consequently, the SFR of RXJ1131 is lower
(cf. SFR\,$>$\,200, with an average of 1200). If we instead adopt the
more generally adopted total IR luminosity
classification (\LIR\,$>$\,10$^{12}$), RXJ1131 would be
considered as a ULIRG given its lensing-corrected
\LIR of $\sim$2\E{12}\,\Lsun.

@@

\subsubsection{Linewidth \& Sizes} %DONE
We find that the linewidths for both components (redshifted and blueshifted)
inferred from a double Gaussian fit to the line profile are
comparable to the C13 ULIRG sample
(FWHM of 370\,\kms). Such linewidths are higher
than local ULIRGs (240\,\kms; \citealt[][]{Solomon97a}).
Since C13 do not have resolved observations, we compare the
gas distribution with local ULIRGs. The CO gas in RXJ1131 is
distributed $\sim$6\,kpc in radius across (in
the source plane), which is more extended than the average in the
sample of disk-like ULIRGs studied by \citet{Ueda14a},
who find an average radius of 3.5\,$\pm$\,2.3\,kpc
with a range spanning 1.1$-$9.3\,kpc.
This is expected if the positive correlation in the linewidth-size relation
holds at intermediate redshifts. Yet we cannot quantify this further
with the data represented in this paper.
